Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-26 VMCAI-revised-version/final.tex
Added new tentative table for results

>>>>

\begin{center}
 \resizebox{\textwidth}{!}{
\begin{tabular}{ | l | c | c | c | r |}
\hline   \
		& WBTS model (with $\Safe = {\uparrow \Safe}$)~ 
		 & Decidability ~ 
 \\ \hline
   \multirow{3}{*}{RP} 
  	& WBTS ($\post$-ideal-effective) Thm~\ref{down-up}
   		 &    \multirow{2}{*}{Decidable}  \\ 
~	& WSTS ($\pred$-basis-effective) Thm~\ref{xxx}
		&  \\\cline{2-3}
~	& WSTS ($\post$-effective) Prop~\ref{indec WSTS} & Undecidable    \\ \hline
   \multirow{3}{*}{BRP} 
  	& WBTS ($\post$-ideal-effective) Thm~\ref{down-up}
   		 & \multirow{2}{*}{Decidable}  \\ 
~	& WSTS ($\pred$-basis-effective) Thm~\ref{xxx}
		&   \\\cline{2-3}
~	&  WSTS ($\pred$-basis-effective) Prop~\ref{indec WSTS}  & Undecidable    \\ \hline
   \multirow{3}{*}{kRP} 
 	& WBTS ($\post$-ideal-effective) Thm~\ref{down-up} 
   		 & \multirow{2}{*}{Decidable}  \\ 
~	& WSTS ($\pred$-basis-effective) Thm~\ref{xxx}
		& \\\cline{2-3}
~	& ? & Undecidable   \\ \hline

   \multirow{2}{*}{sRP} 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{post srp} NON
   		 & Decidable \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & Undecidable   \\ \hline
   \multirow{2}{*}{BsRP} 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{ref ozkan} \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889} 
   		 & Decidable \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & Undecidable    \\ \hline
   \multirow{2}{*}{ksRP} 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{ref ozkan} \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}  
   		 & Decidable \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & Undecidable    \\ \hline

\begin{center}
 \resizebox{\textwidth}{!}{
\begin{tabular}{ | l | c | c | c | r |}
\hline   \ 
		 & WBTS model (with $\Safe = {\downarrow \Safe}$)~ 
		 & Decidability
 \\ \hline
   \multirow{3}{*}{RP} 
   		 & Downard-WSTS ($\pred^*$-basis-effective) Thm~\ref{up-down}
   		 	& \multirow{2}{*}{Decidable}  \\

		& VASS & \\\cline{2-3}
		& Reset-VASS, WSTS ($\pred$-basis-effective) Prop~\ref{indec WSTS with dcs} 
		& Undecidable   \\ \hline
   \multirow{2}{*}{BRP} 
   		 & VASS 
   		 & Decidable   \\\cline{2-3}
~	&  ? & Undecidable    \\ \hline
   \multirow{2}{*}{kRP} 
~	& VASS
		& Decidable \\\cline{2-3}
~	& ? & Undecidable    \\ \hline

   \multirow{2}{*}{sRP} 
   		 & WSTS (downward + upward) Thm~9 & Decidable\\ \cline{2-3}
~	& Reset-VASS, WSTS ($\pred$-basis-effective) Prop~\ref{srp up down}  & Undecidable  \\ \hline
   \multirow{2}{*}{BsRP} 
   		 & WSTS (downward + upward) Cor~\ref{downward brp} & Decidable \\ \cline{2-3}
~	&  ? & Undecidable   \\ \hline
   \multirow{2}{*}{ksRP} 
   		 & WSTS (downward + upward) Cor~\ref{downward brp} & Decidable\\ \cline{2-3}
~	 & ? & Undecidable    \\ \hline
